\section{Background and Related Work}
\label{sec:background}

\subsection{Constant-Time Programming}

A cryptographic implementation is \emph{constant-time} (CT) when execution
behavior is independent of secret data. The discipline targets three features
through which a secret leaks via timing or microarchitectural
state~\cite{kocher}:

\begin{enumerate}
  \item \textbf{Secret-dependent branches:} paths differing in duration or
    branch-predictor state.
  \item \textbf{Secret-dependent memory addresses:} a secret-indexed lookup
    leaves a probeable data-cache footprint.
  \item \textbf{Secret-dependent variable-latency instructions:} cycles depend
    on operands (integer division and modulo are canonical), leaking even with
    fixed control flow and addresses.
\end{enumerate}

Defenses are arithmetic selection, full scans or bit-slicing, and no secrets
in variable-latency instructions. Compilers may reintroduce or relocate a leak,
so CT verification on the shipped binary, under the actual build flags, matters
as much as CT source.

\subsection{The Constant-Time Verification Landscape}

CT checking falls into three groups.

\paragraph{Dynamic taint analysis.}
ctgrind~\cite{ctgrind} marks secrets as uninitialized under Valgrind's
Memcheck~\cite{valgrind}, flagging tainted data in a branch or address -- a
precise binary-level check for the first two classes. Its blind spot is the
third: it passes a secret-dependent division as clean.

\paragraph{Statistical black-box timing.}
dudect~\cite{dudect} applies a Welch $t$-test to cycle counts for fixed versus
random inputs; a difference signals a leak without modeling why. It is
complementary -- catching variable-latency leaks and non-structural effects --
but yields a noise-sensitive judgment, not a proof.

\paragraph{Formal and static analysis.}
ct-verif~\cite{ctverif} verifies CT at the LLVM level by reduction to safety,
and Binsec/Rel~\cite{binsecrel} does relational symbolic execution on binaries.
These give the strongest guarantees but need more setup and again tie ``leak''
to a class.

No single technique covers branches, addresses, variable-latency instructions,
and black-box timing at once; the structural and statistical checks have
disjoint blind spots, motivating binding several checkers together.

\subsection{Constant-Time Concerns in Post-Quantum Cryptography}

CRYSTALS-Kyber~\cite{kyber} and CRYSTALS-Dilithium~\cite{dilithium},
standardized as ML-KEM~\cite{fips203} and ML-DSA~\cite{fips204}, are lattice
schemes whose implementations (e.g.\ PQClean~\cite{pqclean}) contain exactly
the constructs the CT discipline warns about.

KyberSlash~\cite{kyberslash} illustrates this: a division by a public modulus
compiles to a variable-time division on a secret-derived operand. Control flow
and addresses stay constant, so a branch-and-address check reports nothing; the
leak lives in the variable-latency class a Valgrind-style check cannot see.

Yet not every data-dependent timing is a defect. Dilithium signing uses
rejection sampling, so iteration count and time vary by design. FIPS~204
prescribes this, and the variation depends on rejected, non-secret candidates,
not the long-term key. The norm check and hint computation are thus
variable-time \emph{by design} and accepted, not key-recovery leaks;
distinguishing such constructs from genuine leaks requires deliberate triage,
not binary pass/fail.

\subsection{The Gap We Address}

The phenomena are known individually: KyberSlash-style variable-time division,
build-dependence of CT, and dudect detection. Missing is applying the
complementary checkers together, under one configuration and build matrix, and
turning their combined output into a disciplined verdict. Our contribution is
this integration plus a default-deny triage taxonomy separating accepted
variable-time behavior (checked against a cited registry) from a real leak,
never upgrading a finding to a key-recovery claim. The pipeline appears
in Figure~\ref{fig:pipeline}, coverage in Table~\ref{tab:coverage}, and verdict
classes in Table~\ref{tab:corpus}.
